The globular cluster system of the Auriga simulations

### 2019-08-16 AurigaGCS.tex
Updated Figure 2 for #1
Updated Figure 3 for #1

\begin{figure}
    \includegraphics[width=\columnwidth]
        {{MW_RgcFeH_HistogramMassWeighted_Harris1996ed2010data}.png}
    \includegraphics[width=\columnwidth]
        {{M31_RgcFeH_HistogramMassWeighted_CaldwellRomanowsky2016data}.png}
    \caption{
        \emph{Top}: Mass-weighted $R_{\text{gal}}$-[Fe/H] distribution of
        151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H},
        color-coded by the \textbf{median} (values also shown in each bin). The 
        numbers in parenthesis show how many star particles fall within the bin.
        \emph{Bottom}: Same for M31, showing the 366 GCs in CR16 
        \citep[data from][]{2016ApJ...824...42C}. Note that the range of the 
        colourmap differs in both figures.
        \label{fig:observations_FeHRgc}
    }
\end{figure}

@@

\begin{figure*}
    \includegraphics[width=\columnwidth]{{Au4-10_FeH_cleaner-trim}.png}
    \includegraphics[width=\columnwidth]{{Au4-4_and_Au4_21_FeH-trim}.png}
    \caption{
        \emph{Left:} Metallicity distribution of Au4-10 (bottom panel). We show
        the GG candicates in green. We split the GC candidates into two
        subpopulations, those that have formed {\it in~situ} (blue), and those that have
        been accreted (red). The dotted green line shows all star particles.
        The solid purple (magenta) line in the top panel shows the GC system
        of the MW (M31). \emph{Right:} Au4-4 (bottom), and Au4-21 (top).
        \label{fig:Au4-10and21_FeH}
    }
\end{figure*}
We select \mbox{Au4-10}\footnote{The nomenclature is `Au' for Auriga, followed by the
resolution level (4) and halo number (10, indicating which set of initial
conditions was used the run).}, \mbox{Au4-21}, and \mbox{Au4-4} to show the
distributions of three individual simulation runs that we consider representative
for specific behaviour, and to highlight that different runs could give rise to 
different distributions. We plot the age-selected GC candidates in green, those
that are accreted in red, and the {\it in~situ} subpopulation in blue. The top 
half of the left figure shows the MW (M31) GC system in purple (magenta), where 
we overplot a double Gaussian for the MW GCS (the purple dashed lines) by 
adopting literature values of the mean $\mu$ and standard deviation $\sigma$ of 
the metal-rich and metal-poor subpopulations \citep[][p. 38]{Harris2001}.

>>>>

\begin{figure}
    \includegraphics[width=\columnwidth]
        {{MW_RgcFeH_HistogramMassWeighted_Harris1996ed2010data}.png}
    \centering \textcolor{lightgray}{\rule[2mm]{\columnwidth}{0.05mm}}
    \includegraphics[width=\columnwidth]
        {{M31_RgcFeH_HistogramMassWeighted_CaldwellRomanowsky2016data}.png}
    \caption{
        \emph{Top}: Mass-weighted $R_{\text{gal}}$-[Fe/H] distribution of
        151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H},
        color-coded by the \textbf{median} (values also shown in each bin). The 
        numbers in parenthesis show how many star particles fall within the bin.
        \emph{Bottom}: Same for M31, showing the 366 GCs in CR16 
        \citep[data from][]{2016ApJ...824...42C}. Note that the range of the 
        colourmap differs in both figures.
        \label{fig:observations_FeHRgc}
    }
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{FeH_obs_Au4-4_Au4-10_Au4-21}.png}
    \caption{
        \emph{Top}: Metallicity distribution of the MW and M31 GCS. The solid 
        purple (magenta) line shows the GC system of the MW (M31), and we 
        indicate the mean value with an arrow at the bottom of the x-axis. We
        overplot a double Gaussian for the MW GCS using purple dotted lines, taking
        the mean and dispersion from \citep{Harris2001}.
        \emph{Other panels}: three selected Auriga haloes as indicated in the 
        upper right corner. In each of these three panels we show the GG 
        candicates in green, and use a green dotted line for all star particles. 
        We split the GC candidates up into two subpopulations, those that have 
        formed {\it in~situ} (blue), and those that have been accreted (red).
        \label{fig:Au4-10and21_FeH}
    }
\end{figure}
We select \mbox{Au4-10}\footnote{The nomenclature is `Au' for Auriga, followed by the
resolution level (4) and halo number (10, indicating which set of initial
conditions was used the run).}, \mbox{Au4-21}, and \mbox{Au4-4} to show the
distributions of three individual simulation runs that we consider representative
for specific behaviour, and to highlight that different runs could give rise to 
different distributions. We plot the age-selected GC candidates in green, those
that are accreted in red, and the {\it in~situ} subpopulation in blue. The top 
half of the left figure shows the MW (M31) GC system in purple (magenta), where 
we overplot a double Gaussian for the MW GCS (the purple dashed lines) by 
adopting literature values of the mean $\mu$ and standard deviation $\sigma$ of 
the metal-rich and metal-poor subpopulations \citep[][p. 38]{Harris2001}.
